Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
update quote and conclusion

\section{Conclusion and outlook}
As this is the first scalable simulation of molecular energies on any type of quantum hardware it represents an important step in the history of
quantum computing applications. The results indicate that for near-term quantum devices without effective error correction the adaptive approach
represented by the Variational Quantum Eigensolver may have better error resilience than that of standard gate model approach represented by the
Phase Estimation Algorithm. The expectation is that this work will pave the way for the development of further techniques for intractable calculations
 in quantum chemistry. And the final aim is that eventually these variational quantum chemistry techniques will allow for numerically exact simulations
  of chemical reaction rates, which are of great industrial commercial value. In particular, the efficiency - requiring only short state preparation
   and measurement procedures, and so it is without the normal substantial overhead required for quantum error correction - and robustness to
   error displayed by the experimental implementation of the variational quantum eigensolver technique indicates that this technique might succeed
    where classical techniques fail in solving traditionally intractable problems.

Late last year the US passed the new National Quantum Initiative Act pledging around \textdollar1.2 billion in funding for quantum information science
 \cite{usbill}. At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top
 European researchers in quantum technologies over the next decade \cite{eubill}. In the UK, the EPSRC-backed Quantum Technology Hubs represent
 part of a £270 million investment to create national networks of quantum expertise \cite{ukbill}. With this extraordinary push of late across
 Europe and also in the US and China, aiming to fast-track quantum technologies out of university research groups and into industrial applications,
 the importance of this work in quantum chemistry simulations cannot be overstated. As aside from the much touted almost pop-science status of
 quantum encryption, the myriad opportunities afforded by more efficient scalable quantum chemistry simulations looms large in garnering serious
 investor interest. The ability to run quantum simulations of the behaviour of molecules and materials is hoped offer new avenues for increasing
 our understanding of chemistry and enable the development of new medicines and materials in silico.

>>>>

\section{Conclusion and outlook}

As this is the first scalable simulation of molecular energies on any type of quantum hardware it represents an important step in the history of
quantum computing applications. The results indicate that for near-term quantum devices without effective error correction the adaptive approach
represented by the Variational Quantum Eigensolver may have better error resilience than that of standard gate model approach represented by the
Phase Estimation Algorithm. The expectation is that this work will pave the way for the development of further techniques for intractable calculations
 in quantum chemistry. And the final aim is that eventually these variational quantum chemistry techniques will allow for numerically exact simulations
  of chemical reaction rates, which are of great industrial commercial value. In particular, the efficiency - requiring only short state preparation
 and measurement procedures, and so it is without the normal substantial overhead required for quantum error correction - and robustness to
 error displayed by the experimental implementation of the variational quantum eigensolver technique indicates that this technique might succeed
 where classical techniques fail in solving traditionally intractable problems.

 Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that "variational techniques in quantum chemistry
 are becoming increasingly prevalent as a useful benchmarking tool these early stage Quantum devices, and this paper by O’Malley et al.
 represents one of the most accurate quantum chemistry simulations using quantum hardware to date, and is a certainly a promising validation of the
  development of superconducting qubits for scalable quantum hardware".

Late last year the US passed the new National Quantum Initiative Act pledging around \textdollar1.2 billion in funding for quantum information science
 \cite{usbill}. At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top
 European researchers in quantum technologies over the next decade \cite{eubill}. In the UK, the EPSRC-backed Quantum Technology Hubs represent
 part of a £270 million investment to create national networks of quantum expertise \cite{ukbill}. With this extraordinary push of late across
 Europe and also in the US and China, aiming to fast-track quantum technologies out of university research groups and into industrial applications,
 the importance of this work in quantum chemistry simulations cannot be overstated. As aside from the much touted almost pop-science status of
 quantum encryption and communication, the myriad opportunities afforded by more efficient and scalable quantum chemistry simulations looms large
 in garnering serious investor interest. The ability to run quantum simulations of the behaviour of molecules and materials is hoped offer new
 avenues for increasing our understanding of chemistry and enable the development of new medicines and materials in silico.
